Rotations and Insecticide Resistance initial plots

### 2017-10-10 inst/documents/rotations1.Rmd
improve UI and plots add log scale option

>>>>

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="Showing how with cost (0.1) an initial decline in the freq of the later insecticides when they are not being used can lead them to behave differently than earlier ones."}

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.show='hold', fig.align='left', fig.cap="When cost is set to 0 all insecticides give the same curves."}

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

### 2017-10-10 inst/documents/rotations_notes.Rmd
improve UI and plots add log scale option

*9/10/17*
~ started first shiny UI : rotresist1
~ add rot interval and generations to rotresist

@@

e.g. :
run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.01 , rotation_interval = 50 , eff = 0.7 , dom = 0.5 , rr = 0.5 , expo_hi = 0.7 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

@@

~ test setting inputs correctly (move away from hardcoded test functions)
~ find what went wrong when I set fitnesses
~ get Ian to pull changes

>>>>

*9/10/17*
~ started first shiny UI : rotresist1
~ add rot interval and generations to rotresist
~ looking good

*10/10/17*

~ aha! the new UI helped me to see that this can be a result of the decline in resistance frequency for the later insecticides when they are not being used at the start. e.g.

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0.1 )

When cost is set to 0 all 3 insecticides give the same curves :

run_rot( n_insecticides = 3 , max_generations = 150 , start_freqs = 0.1 , rotation_interval = 50 , eff = 0.6 , dom = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0.8 , migration_rate_intervention = 0.01 , cost = 0 )

done ~ in plots change r1 to insecticide_1 etc.
done ~ in plots add the deployment symbol to legend

done ~ can I offer option to have plots on log y axis to make it clearer whats going on at lower frequencies ?

Now from the UI ticking log y axis influences the next plot, (but is isolated so allows you to compare log & non log plots).

Starting to think about sensitivity analysis.
For Levick et al the inputs and ranges were hardcoded into resistance::sensiAnPaperPart()

start_freq |    0.0001 - 0.1 log uniform
exposure |      0.1 - 0.9
male_exposure | 0 - 1
effectiveness | 0.3 - 1
dominance     | 0 - 1
rr_restoration |  0.2 - 1
correct_mix   | 0.5 - 1

To add for rotations

n_insecticides    | 
max_generations   | 
rotation_interval | 
coverage          | 
migration         |  
cost              |

@@

~ meet with Ian PM to prepare table for sensitivity analysis, we'll need to think about num insecticides, num generations & coverage too

~ what were the ranges for the Levick paper

~ Ian said we may want to 
~ Ian will send me grant app to assess single v multi locus insecticide resistance
~ Ian said we may want to put something in to stop Frequency going below initial starting value when not in use (because this could represent background balance between benefits & cost)

@@

~ get Ian to pull changes
